
```{r setup, echo=FALSE, include=FALSE, cache=FALSE}
# Set up the environment
library(knitr) 
opts_chunk$set(cache.path='cache/', fig.path='img/', cache=F, tidy=T, fig.keep='high', dpi=300, out.width=700, echo=F, autodep=T)
options(replace.assign=TRUE, width=120)
set.seed(1)
```

```{r analysis}
# The results of GenomeRunner analyses are stored in category-specific folders, 
# e.g. "GR.altSplicing". Sets of categories may be analyzed separately, and the results
# may be stored in different folders, e.g. "data.gfs", "data.enc"
# Changing the analysisType will process the results from the corresponding folder
analysisType <- "data.gfs"
```

Hispanic SNP sets analysis, `r if (analysisType == "data.gfs") {"custom"} else {"ENCODE"}` genome annotation data
========================================================
 
```{r loadLibraries, warning=FALSE, message=FALSE}
# Filters non-significant rows from a matrix
mtx.filter <- function(x, pval=0.01){
  idx <- as.logical(abs(rowMeans(x)) < pval)
  tmp <- as.matrix(x[idx, ])
  colnames(tmp) <- colnames(x)
  rownames(tmp) <- rownames(x)[idx]
  idxEnrich <- as.logical(rowMeans(tmp) > 0)
  tmp1 <- as.matrix(tmp[idxEnrich, ])
  colnames(tmp1) <- colnames(tmp)
  rownames(tmp1) <- rownames(tmp)[idxEnrich]
  idxDeplet <- as.logical(rowMeans(tmp) <= 0)
  tmp2 <- as.matrix(tmp[idxDeplet, ])
  colnames(tmp2) <- colnames(tmp)
  rownames(tmp2) <- rownames(tmp)[idxDeplet]
  if (nrow(tmp1) > 1) tmp1 <- tmp1[order(tmp1[, 1], decreasing=F), ]
  if (nrow(tmp2) > 1) tmp2 <- tmp2[order(tmp2[, 1], decreasing=T), ]
  return(list(as.matrix(tmp1), as.matrix(tmp2)))
}
```

```{r loadData}
dirs <- list.dirs(analysisType, full.names=T, recursive=F) # Paths the SNP sets analyses
analyses <- list() # Empty list to hold analyses paths 
for (d in dirs) {
  analyses <- c(analyses, list(list.dirs(d, full.names=T, recursive=F)))
}
```

Double lines (===) mark the names of the regions being analyzed. 

Pluses (+++) mark the names of categories of genomic features, used for the enrichment analysis

Cell type-specific sets of epigenomic elements from the ENCODE project were used.

For each analysis, only the significant enrichment results (p < 0.01) are shown. If an analysis does not have any significant results, it is not displayed at all. The analyses are separated by single lines (---).

Negative p-value indicates depletion.

```{r showData}
#length(dirs)
for (d in 1:length(dirs)) {
  print("===============================================================")
  print(paste("Region analyzed:", dirs[d]))
  print("===============================================================")
  for (a in unlist(analyses[d])) {
      mtx <- (read.table(paste(a, "matrix.txt", sep="/"), sep="\t", row.names=1, header=T))
      mtx <- mtx.filter(mtx)
      numEnrich <- nrow(mtx[[1]])
      numDeplet <- nrow(mtx[[2]])
      if (numEnrich > 0) {
        print("+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++")
        print(paste("Category of genomic features:", a))
        print("+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++")
        print(paste("The total number of significantly ENRICHED associations is:", numEnrich,  "Top 10, or less, are shown"))
        if (numEnrich > 10) numEnrich <- 10
        if (numEnrich == 1) {
          print(data.frame(Enrich.pval=format(mtx[[1]], digits=3, scientific=T), row.names=rownames(mtx[[1]])))
        } else {
          print(data.frame(Enrich.pval=format(mtx[[1]][1:numEnrich, ], digits=3, scientific=T)))
        }
        print("---------------------------------------------------------------")
        #grid.table(mtx)
      }
      if (numDeplet > 0) {
        print(paste("The total number of significantly DEPLETED associations is:", numDeplet, "Top 10, or less, are shown"))
        if (numDeplet > 10) numDeplet <- 10
        if (numDeplet == 1) {
          print(data.frame(Deplet.pval=format(mtx[[2]], digits=3, scientific=T), row.names=rownames(mtx[[2]])))
        } else {        
          print(data.frame(Deplet.pval=format(mtx[[2]][1:numDeplet, ], digits=3, scientific=T)))
        }
        print("---------------------------------------------------------------")
        #grid.table(mtx)
    }
  }
}
```


